Vertical shear instability in astrophysical disks: vertically global linear calculations with thermal relaxation and applications to the Solar Nebula

### 2015-03-14 numerical.tex
updating

\subsubsection{Comment on `surface modes'} 
Our fiducial setup with $\khat=10$ in 
Fig. \ref{compare_modes_iso_kx10} (black dots) differs to that from
\cite{nelson13} and \cite{mcnally14} in the lack of `surface modes'. 
These modes lie almost parallel to the vertical axis in mode 
diagrams such as Fig. \ref{compare_modes_iso_kx10}. We find them for 
sufficiently large $\zmax$ and/or $\khat$. % For example, the two
% largest growth rates found for the case with $\zmax=7H$ in
% Fig. \ref{compare_modes_iso_kx10} are surface modes.

@@

For $5\lesssim\khat\lesssim30$, we find $\beta_\mathrm{crit}$ provides
an accurate prediction of the upper limit to the thermal relaxation 
timescale for the fundamental mode. For smaller $\khat$, the VSI can
operate slightly beyond $\beta_\mathrm{crit}$ (recall that
$\beta_\mathrm{crit}$ was derived by assuming $\khat^2\gg 1$). For
$\khat\geq 50$, we find perturbations have large amplitudes near the
vertical boundaries, and complications to our numerical search of
eigenvalues arise from emergence of modes associated with boundary
conditions. Nevertheless, growth rates rapidly decrease as $\beta$
approaches and increase beyond $\beta_\mathrm{crit}$.

@@

\begin{figure}
   \includegraphics[width=\linewidth]{figures/gcorr_compare2} 
   \caption{Growth rate of the fundamental VSI mode in the fiducial disk
     model as a function of the thermal relaxation timescale $\beta$
     The vertical line is the critical thermal timescale
     $\beta_\mathrm{crit}$ obtained 
     from Eq. \ref{iso_vsi_cond}. 
     \label{bcrit_compare1}}   
 \end{figure}

>>>>

\subsubsection{Comment on `surface modes'}\label{surf_comment}
Our fiducial setup with $\khat=10$ in 
Fig. \ref{compare_modes_iso_kx10} (black dots) differs to that from
\cite{nelson13} and \cite{mcnally14} in the lack of `surface modes'. 
These modes lie almost parallel to the vertical axis in mode 
diagrams such as Fig. \ref{compare_modes_iso_kx10}. We find them for 
sufficiently large $\zmax$ and/or $\khat$. % For example, the two
% largest growth rates found for the case with $\zmax=7H$ in
% Fig. \ref{compare_modes_iso_kx10} are surface modes.

@@

For $5\lesssim\khat\lesssim30$, we find $\beta_\mathrm{crit}$ provides
an accurate prediction of the upper limit to the thermal relaxation 
timescale for the fundamental mode. For smaller $\khat$, the VSI can
operate slightly beyond $\beta_\mathrm{crit}$ (recall that
$\beta_\mathrm{crit}$ was derived by assuming $\khat^2\gg 1$). For
$\khat\geq 50$, we find perturbations have large amplitudes near the
 vertical boundaries, and 
complications to our numerical search of
eigenvalues arise from the emergence of modes associated with boundary
conditions. Nevertheless, growth rates rapidly decrease as $\beta$
approaches and increase beyond $\beta_\mathrm{crit}$.

@@

\begin{figure}
   \includegraphics[width=\linewidth]{figures/gcorr_compare2} 
   \caption{VSI growth rates in the fiducial disk
     model as a function of the thermal relaxation timescale
     $\beta$. These are obtained by following the eigenvalues of the
     fundamental mode at $\beta=10^{-3}$. The vertical line is the
     critical thermal timescale $\beta_\mathrm{crit}$ obtained  
     from Eq. \ref{iso_vsi_cond}. 
     \label{bcrit_compare1}}   
 \end{figure}
